\documentclass[a4paper,10pt]{article}
\usepackage[top=3cm, bottom=3cm, left=3cm, right=3cm]{geometry} 
% \usepackage{helvet} \renewcommand{\familydefault}{\sfdefault}
\title{Curriculum - Paulo Costa}
\author{Paulo Costa}  
\usepackage[utf8]{inputenc}
\begin{document}  
  \LARGE\textbf{Paulo Roberto de Almeida Costa}

  \large me@paulo.costa.nom.br

  \large Phone: +55 (19) 9345-6800

  \large Campinas - SP - Brazil

  \normalsize 
  \section{Education}
    \begin{itemize}
      \item  
        \textbf{Computer Engineering} - IC/Unicamp

        Study Certificates:
        \begin{itemize}
          \item Visual Computing
          \item Project of Dedicated Hardware Systems
          \item Software Engineering
          \item Project of Information Systems
        \end{itemize}

        March/2006 to December/2010.

%       \item  
%         \textbf{Computer Science} - IC/Unicamp
% 
%         Period: August/2011 to June/2013 (Expected).

      \item  
        \textbf{Technician in Eletronics} - Cotuca/Unicamp

        February/2007 to December/2010.

      \item  
        \textbf{Technician in Informatics} - Cotuca/Unicamp

        Emphasis in Support Systems

        February/2003 to December/2006.

    \end{itemize}

  \section{Professional Experience}
    \begin{itemize}
      \item  
        \textbf{Facebook}, Software Engineer
        
        October/2012 to present.

        \item  
        \textbf{Veridis Tecnologia}, Software Engineer

        September/2009 to October/2012.

      \item  
        \textbf{Griaule Biometrics}, Software Engineer

        May/2006 to September/2009.

      \item
        \textbf{CPqD - Research and Development Center in Telecomunications}, Software Engineering Intern

        December/2005 to February/2006.
    \end{itemize}

  \section{Spoken Languages}
    \begin{itemize}
      \item  
        \textbf{English} - Advanced Level.

        109/120 points on TOEFL iBT (November/2008).

      \item  
        \textbf{Portuguese} - Native Speaker.
    \end{itemize}

\end{document}
